|

### 2023-03-17 paper/01-introduction.Rmd
Add bdb intro with text about previous work to transition into pass rush metrics

# Introduction {#sec:introduction}

@@

The National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016
BDB
https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/

>>>>

---
output:
  html_document: default
  pdf_document: default
---
# Introduction {#sec:introduction}

@@

We contribute to the growing literature of research based on player tracking data in American football. The National Football League (NFL) introduced their player tracking system known as [Next Gen Stats (NGS)](https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/) in 2016, using radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data 10 times per second. These NGS tracking data contain information about the on-field locations, speeds, and angles of all 22 players on the field (as well as the ball). While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual [Big Data Bowl (BDB)](https://operations.nfl.com/gameday/analytics/big-data-bowl/past-big-data-bowl-recaps/) competition.

The first BDB led to several contributions largely focused offensive performance evaluation. For example. finalists @deshpande2020expected introduced an approach for modeling the hypothetical completional probability of a pass aiding in the evalaution of quarterback (QB) decision making. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going]. Since its inception, the BDB has changed themes each year leading to new insight about evaluating running backs, defensive backs, and special teams performance.

In this work, we present a novel approach to measure the performance of pass rushers (defensive players charging the QB) that was selected as a finalist for the [2023 edition of the NFL BDB](https://www.kaggle.com/competitions/nfl-big-data-bowl-2023), which asked participants to evaluate linemen on passing plays. Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.
